### 2016-01-05 p2/abstract.tex
Renamed directories

These results are often intuitive,
but providing exact proofs for them is far from trivial.
They contribute to our understanding of this special type of algebraic model,
and toward building a more complete algebra
of filesystems and other storage protocols.
They also form a theoretical basis for
specifying
and guaranteeing the error-free operation
of applications that implement operation-based approaches to synchronization.

>>>>

These results are often intuitive,
but providing exact proofs for them is far from trivial.
They contribute to our understanding of this special type of algebraic model,
and toward building a more complete algebra
of filesystems and other storage protocols.
They also form a theoretical basis for
specifying
and guaranteeing the error-free operation
of applications that implement an algebraic approach to synchronization.

### 2016-01-05 p2/axioms.tex
Renamed directories

We methodically investigated of all possibilities using a computer 
program\footnote{The program is accessible on-line at \\
https://github.com/csirmaz/AlgebraicSyncPaper/blob/master/ii/prove.py.}
to determine
which pairs of commands cause errors all the time,
which can be simplified to one or no commands, and which can be reversed
without any change in their overall effect.
Our basis for this investigation was the model of filesystems introduced in this paper.
These properties of command pairs are crucial as they determine
how a set of commands can be re-ordered to be applied to a filesystem
during synchronization, and what commands will never be compatible.
Below we list a number of statements derived using this method.

>>>>

We methodically investigated of all possibilities using a computer 
program\footnote{The program is accessible on-line at \\
https://github.com/csirmaz/AlgebraicSyncPaper/blob/master/p2/prove.py.}
to determine
which pairs of commands cause errors all the time,
which can be simplified to one or no commands, and which can be reversed
without any change in their overall effect.
Our basis for this investigation was the model of filesystems introduced in this paper.
These properties of command pairs are crucial as they determine
how a set of commands can be re-ordered to be applied to a filesystem
during synchronization, and what commands will never be compatible.
Below we list a number of statements derived using this method.

### 2016-01-05 p2/conclusion.tex
Renamed directories

Apart from constructing an algebra,
there are many other ways in which further work can extend the current results.
We think one of the most interesting extensions would be to
consider reconciling not only two, but more replicas in a single step and
prove the correctness and maximality of the algorithm proposed.
A related problem is to model cases where reconciliation cannot
complete fully (due to a system or network failure, for example)
or if only a subset of the replicas are reconciled,
both of which would result in a state where different replicas
have different common ancestors, that is,
the updates specific to the replicas start from different points
in the update history of the filesystem.
Identifying the information one needs to keep to perform
update detection in such cases and devising a suitable algorithm
would be beneficial for any implementation of a reconciler
based on the ideas presented here.

>>>>

Apart from constructing an algebra,
there are many other ways in which further work can extend the current results.
We think one of the most interesting extensions would be to
consider reconciling not only two, but more replicas in a single step and
prove the correctness and maximality of the algorithm proposed.
A related problem is to model cases where reconciliation cannot
complete fully
or if only a subset of the replicas are reconciled 
(e.g. due to network partitioning),
both of which would result in a state where different replicas
have different common ancestors, that is,
the updates specific to the replicas start from different points
in the update history of the filesystem.
Parker et al. (\cite{PPRS}) and Cox and Josephson (\cite{CJ})
describe version vectors (update histories) kept as metadata that could solve this problem.
Extending the algebraic approach to represent individual updates to files
in their modification histories (as described in \cite{CJ})
as separate commands could also enable it to reconcile otherwise
conflicting updates and resolve partial reconciliations.

### 2016-01-05 p2/def-filesystem.tex
Renamed directories

We model a working filesystem
using a function $\FS$ with a set of nodes (filesystem paths) $\setn$ as its domain,
and a set of possible contents or values $\setv$ as its codomain.
Alternatively, if the filesystem has encountered a problem and is no longer usable, 
we assign it the special value $\fsbroken$:
\begin{mydef}[Filesystem]
\begin{gather*}
\FS =
\begin{cases}
\setn \rightarrow \setv \\
\fsbroken
\end{cases}
\end{gather*}
\end{mydef}
In our model, $\setn$ 
serves as a namespace or ``skeleton'' for the filesystem, and it
contains all possible nodes, including the ones where there is no file or directory,
which we denote using a special value $\empt\in\setv$.

>>>>

We model a working filesystem
using a function $\FS$ with a set of nodes (filesystem paths) $\setn$ as its domain,
and a set of possible contents or values $\setv$ as its codomain.
Alternatively, if the filesystem has encountered a problem and is no longer usable, 
we assign it the special value $\fsbroken$:
\begin{mydef}[Filesystem]
\begin{gather*}
\FS =
\begin{cases}
\setn \rightarrow \setv \\
\fsbroken
\end{cases}
\end{gather*}
\end{mydef}
In our model, $\setn$ 
serves as a namespace or ``skeleton'' for the filesystem.
It contains all possible nodes, including the ones 
where the file system contains no file or directory,
where in our model $\FS$ has a special value, $\empt\in\setv$.

### 2016-01-05 p2/intro.tex
Renamed directories

In this paper we investigate an operation- or command-based approach
to synchronizing filesystem trees.
Presented with multiple copies (replicas) of the same filesystem that have been independently modified,
we regard the aim of the synchronizer to modify these replicas further
to make them as similar as possible.
The synchronization algorithm we describe
follows the two main steps described by Balasubramaniam and Pierce (\cite{BP}):
update detection, where we identify modifications that have been applied to the replicas
since they diverged,
and reconciliation, where we identify updates that can be propagated to other replicas and do so.
The remaining updates, which could not be propagated, are conflicting updates;
resolving these requires a separate system or human intervention.

In this paper we build on our previous work done 
with Prof. Norman Ramsey
on an algebraic approach to synchronization
(\cite{NREC}),
and add to the theoretical understanding
of synchronization by providing rigorous proofs that the algorithms
we describe work as intended
and offer a solution in our framework that cannot be improved on.

>>>>

In this paper we investigate a command-based approach
to synchronizing filesystem trees.
Presented with multiple copies (replicas) of the same filesystem that have been independently modified,
we regard the aim of the synchronizer to modify these replicas further
to make them as similar as possible.
The synchronization algorithm we describe
follows the two main steps described by Balasubramaniam and Pierce (\cite{BP}):
update detection, where we identify modifications that have been applied to the replicas
since they diverged,
and reconciliation, where we identify updates that can be propagated to other replicas and do so.
The remaining updates, which could not be propagated, are conflicting updates;
resolving these requires a separate system or human intervention.

In this paper we build on previous work done 
by Ramsey and Csirmaz
on an algebraic approach to synchronization
(\cite{NREC}),
and add to the theoretical understanding
of synchronization by providing rigorous proofs that the algorithms
we describe work as intended
and offer a solution in our framework that cannot be improved on.

### 2016-01-05 p2/rec-complete.tex
Renamed directories

First, we prove that this sequence breaks all filesystems
unless $n=m$.
Let us therefore suppose $n\neq m$ and, to use an inverse proof,
that the sequence works on $\FS$ where $A\FS\neq\fsbroken$.
If so, its initial segment, $\acb\cc S_0\cc T_0 \cc \czwmv \cc \cxynv$ must also work.

@@

On the one hand we therefore know that $\FS(m)$ must be of type $Z$,
but on the other, from \cref{ax_directchild_breaks,ax_directparent_breaks},
we also know that $\cxynv$ cannot be applied to $\FS$ without
changing $\FS(m)$ first.
As $A\FS\neq\fsbroken$, this means that $A$ must contain a command on $m$.
Let this command be $\cqrmv$.

>>>>

First, we prove that this sequence breaks all filesystems
unless $n=m$.
Let us therefore suppose $n\neq m$ and, to use an inverse proof,
that the sequence works on $\FS$ where $A\aFS\neq\fsbroken$.
If so, its initial segment, $\acb\cc S_0\cc T_0 \cc \czwmv \cc \cxynv$ must also work.

@@

On the one hand we therefore know that $\FS(m)$ must be of type $Z$,
but on the other, from \cref{ax_directchild_breaks,ax_directparent_breaks},
we also know that $\cxynv$ cannot be applied to $\FS$ without
changing $\FS(m)$ first.
As $A\aFS\neq\fsbroken$, this means that $A$ must contain a command on $m$.
Let this command be $\cqrmv$.

### 2016-01-05 p2/upd-correct.tex
Renamed directories

Based on \cref{ax_same_emptyseq,ax_same_singlec} there is
an $S''\eqnrw S'$ in which multiple commands on the same nodes
are simplified into a single command or an empty sequence,
and therefore $S''$ is simple and $S\equiv S'\eqext S''$.
It is easy to see that $S''$ must contain the same commands
as the output of the update detector, $U$, as both are simple
but reflect all changes between $\FS$ and $\FS^*$.
If so, then $S''\in\orderset{U}$ and based on \cref{simple_reorder_equiv}
we have
$S\equiv S'\eqext S''\equiv U$, and as $S\aFS = \FS^* \neq \fsbroken$,
therefore $U\aFS\neq\fsbroken$.
\end{proof}

>>>>

Applying \cref{ax_same_emptyseq,ax_same_singlec} we can
convert $S'$ into
an $S''\eqnrw S'$ in which multiple commands on the same nodes
are simplified into a single command or an empty sequence,
and therefore $S''$ is simple and $S\equiv S'\eqext S''$.
It is easy to see that $S''$ must contain the same commands
as the output of the update detector, $U$, as both are simple
but reflect all changes between $\FS$ and $\FS^*$.
If so, then $S''\in\orderset{U}$ and based on \cref{simple_reorder_equiv}
we have
$S\equiv S'\eqext S''\equiv U$, and as $S\aFS = \FS^* \neq \fsbroken$,
therefore $U\aFS\neq\fsbroken$.
\end{proof}

An important consequence of this proof is that any sequence
of recorded updates that were applied to a filesystem can be
converted to a simple sequence using the rules listed in
\cref{section_axioms} alone.
